Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-05-11 krs-survey.tex
Better use of tikz to style taxonomy nodes

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, level distance = 3cm, level 1/.style={sibling distance=5mm}]
    %[edge from parent fork east]
    %every node/.style={fill=black!30,rounded corners},
    %[parent anchor=east,child anchor=west,grow=east,
    %edge from parent/.style={thick,draw}]
    \node {Dimensions}
        child {node {{\bf F}. Instantiation}}
        child {node {{\bf E}. Integration}}
        child {node {{\bf D}. Acquisition}}
        child {node {{\bf C}. Reasoning}}
        child {node {{\bf B}. Representation}}
        child {node {{\bf A}. Expressiveness}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3.5cm]
    \node {\bf A. Expressiveness}
            child {node {{\bf A.5}. Meta-cognition}}
            child {node {{\bf A.4}. Uncertainty}}
            child {node {{\bf A.3}. OWA/CWA}}
            child {node {{\bf A.2}. Expressive power}}
            child {node {{\bf A.1}. Logic formalism}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3cm]
    \node {\bf B. Representation}
            child {node {{\bf B.5}. Memory}}
            child {node {{\bf B.4}. Introspection}}
            child {node {{\bf B.3}. Possible Worlds}}
            child {node {{\bf B.2}. Context}}
            child {node {{\bf B.1}. Roles}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 4cm]
    \node {\bf C. Reasoning}
            child {node {{\bf C.10}. Learning}}
            child {node {{\bf C.9}. Naive physics}}
            child {node {{\bf C.8}. Planning}}
            child {node {{\bf C.7}. Prediction}}
            child {node {{\bf C.6}. Presupposition}}
            child {node {{\bf C.5}. Non-monotonicity}}
            child {node {{\bf C.4}. Uncertainty}}
            child {node {{\bf C.3}. Lazy evaluation}}
            child {node {{\bf C.2}. Structural alteration}}
            child {node {{\bf C.1}. Standard reasoning}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3cm]
    \node {\bf D. Acquisition}
            child {node {{\bf D.4} Dynamic instantiation}}
            child {node {{\bf D.3} Motivation}}
            child {node {{\bf D.2} Grounding}}
            child {node {{\bf D.1} Acquisition and fusion}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3cm]
    \node {\bf D.1 Acquisition and fusion}
            child {node {{\bf D.1.3} Linked Resources}}
            child {node {{\bf D.1.2} Interaction}}
            child {node {{\bf D.1.1} Sensing}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3cm]
    \node {\bf E. Integration}
            child {node {{\bf D.5} Performances}}
            child {node {{\bf D.4} Monitoring}}
            child {node {{\bf D.3} Natural Language}}
            child {node {{\bf D.2} Executive layers}}
            child {node {{\bf D.1} Sensori-motor}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3.5cm]
    \node {\bf D.5 Performance Evaluation}
            child {node {{\bf D.5.2} Cognitive Performances}}
            child {node {{\bf D.5.1} Raw Performances}};
 \end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3.5cm]
    \node {\bf F. Knowledge instantiation}
            child {node {{\bf F.4} Alignement with Standards}}
            child {node {{\bf F.3} Self-Knowledge}}
            child {node {{\bf F.2} Metrics}}
            child {node {{\bf F.1} Design Strategy}};
 \end{tikzpicture}
\end{center}
\end{scriptsize}

>>>>

\tikzstyle {taxonomy} = [grow=right, level distance = 3cm, sibling distance=7mm]
\tikzstyle {completetaxonomy} = [grow=right]
\tikzstyle {taxon} = [text width=3cm, text centered,inner sep=0pt, outer sep=2pt] %, draw=blue!50,thick]

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[taxonomy]
    %[edge from parent fork east]
    %every node/.style={fill=black!30,rounded corners},
    %[parent anchor=east,child anchor=west,grow=east,
    %edge from parent/.style={thick,draw}]
    \node [taxon] {Dimensions}
        child {node [taxon] {{\bf F}. Instantiation}}
        child {node [taxon] {{\bf E}. Integration}}
        child {node [taxon] {{\bf D}. Acquisition}}
        child {node [taxon] {{\bf C}. Reasoning}}
        child {node [taxon] {{\bf B}. Representation}}
        child {node [taxon] {{\bf A}. Expressiveness}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[taxonomy]
    \node [taxon] {\bf A. Expressiveness}
            child {node [taxon] {{\bf A.5}. Meta-cognition}}
            child {node [taxon] {{\bf A.4}. Uncertainty}}
            child {node [taxon] {{\bf A.3}. OWA/CWA}}
            child {node [taxon] {{\bf A.2}. Expressive power}}
            child {node [taxon] {{\bf A.1}. Logic formalism}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[taxonomy]
    \node [taxon] {\bf B. Representation}
            child {node [taxon] {{\bf B.5}. Memory}}
            child {node [taxon] {{\bf B.4}. Introspection}}
            child {node [taxon] {{\bf B.3}. Possible Worlds}}
            child {node [taxon] {{\bf B.2}. Context}}
            child {node [taxon] {{\bf B.1}. Roles}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[taxonomy]
    \node [taxon] {\bf C. Reasoning}
            child {node [taxon] {{\bf C.10}. Learning}}
            child {node [taxon] {{\bf C.9}. Naive physics}}
            child {node [taxon] {{\bf C.8}. Planning}}
            child {node [taxon] {{\bf C.7}. Prediction}}
            child {node [taxon] {{\bf C.6}. Presupposition}}
            child {node [taxon] {{\bf C.5}. Non-monotonicity}}
            child {node [taxon] {{\bf C.4}. Uncertainty}}
            child {node [taxon] {{\bf C.3}. Lazy evaluation}}
            child {node [taxon] {{\bf C.2}. Structural alteration}}
            child {node [taxon] {{\bf C.1}. Standard reasoning}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[taxonomy]
    \node [taxon] {\bf D. Acquisition}
            child {node [taxon] {{\bf D.4} Dynamic instantiation}}
            child {node [taxon] {{\bf D.3} Motivation}}
            child {node [taxon] {{\bf D.2} Grounding}}
            child {node [taxon] {{\bf D.1} Acquisition and fusion}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[taxonomy]
    \node [taxon] {\bf D.1 Acquisition and fusion}
            child {node [taxon] {{\bf D.1.3} Linked Resources}}
            child {node [taxon] {{\bf D.1.2} Interaction}}
            child {node [taxon] {{\bf D.1.1} Sensing}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[taxonomy]
    \node [taxon] {\bf E. Integration}
            child {node [taxon] {{\bf D.4} Performances}}
            child {node [taxon] {{\bf D.3} Monitoring}}
            child {node [taxon] {{\bf D.2} Executive layers}}
            child {node [taxon] {{\bf D.1} Sensori-motor}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[taxonomy]
    \node [taxon] {\bf D.5 Performance \\Evaluation}
            child {node [taxon] {{\bf D.5.2} Cognitive Performances}}
            child {node [taxon] {{\bf D.5.1} Raw Performances}};
 \end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[taxonomy]
    \node [taxon] {\bf F. Knowledge instantiation}
            child {node [taxon] {{\bf F.4} Alignement with Standards}}
            child {node [taxon] {{\bf F.3} Self-Knowledge}}
            child {node [taxon] {{\bf F.2} Metrics}}
            child {node [taxon] {{\bf F.1} Design Strategy}};
 \end{tikzpicture}
\end{center}
\end{scriptsize}
